%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\cventry
    {Full-Stack Developer} % Job title
    {Würth S.r.l.} % Organization
    {Egna (BZ), Italy} % Location
    {Jul. 2025 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of full-stack solutions for internal company use.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Developer} % Job title
    {(Internship) Cherry Chain S.R.L.} % Organization
    {Povo (TN), Italy} % Location
    {Jul. 2024 - Nov. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Redesign and normalization of a database schema for a loyalty card management project for DAO.}
        \item {Reimplementation of key endpoints following UAT (User Acceptance Tests) using TDD (Test Driven Development) and DDD (Domain Driven Design) techniques.}
        \item {Development of Web APIs in Kotlin with Helidon for handling loyalty card subscription and data update operations.}
        \item {Use of Flyway for database migrations and versioning on a PostgreSQL instance based on the new schema.}
        \item {Design and development of the back-office UI used by DAO employees, utilizing HTMX and TailwindCSS, served by the Helidon server.}
        \item {Deepening of authentication concepts for future project developments.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Minecraft Mod Developer} % Job title
    {Sbriser SRL}% Organization
    {Italy (Full Remote)} % Location
    {Mar. 2021 - Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of mods for the videogame Minecraft with Java and Carpet Script (scarpet)}
        \item {Uploading game files to remote FTP server with Filezilla}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Minecraft Mod Developer} % Job title
    {TheMark di Marco Totaro} % Organization
    {Italy (Full Remote)} % Location
    {May 2020 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of mods for the videogame Minecraft with MCreator, Java and Carpet Script (scarpet)}
      \end{cvitems}
    }
\end{cventries}