%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry {\href{https://github.com/Festa-di-Primavera/fdp-app}{GitHub: fdp-app}} % Job title
  {Ticket Management System for "Festa di Primavera" (Spring Party)} % Organization
  {Trento, Italy} % Location
  {Jan. 2024 - Mar. 2024} % Date(s)
  { \begin{cvitems} % Description(s) of tasks/responsibilities
  \item {Designed and developed the web application for managing ticket sales and validation for the annual Spring Festival organized by C.U.S. Trento.} \item {Implemented responsive front-end features using SvelteKit, leveraging UI libraries such as Tailwind CSS and Flowbite for an optimized user experience.} \item {Developed back-end APIs and integrated Firebase for authentication and real-time database management, ensuring secure and seamless operations.}\end{cvitems} }

  %---------------------------------------------------------
  \cventry
  { \href{https://github.com/PTZ-Vision/PTZ-Vision-Android}{GitHub: PTZ Vision}} % Job title
  {PTZ Camera Remote Control} % Organization
  {Trento, Italy} % Location
  {May 2024 - Sep. 2024} % Date(s)
  { \begin{cvitems}\item {Led the architecture design of the project, implementing the MVVM pattern for scalability and maintainability.} \item {Developed intuitive and responsive UI/UX using Kotlin Jetpack Compose, with a focus on modular component separation.} \item {Integrated local data persistence for camera settings through Room Database (SQLite), enabling efficient and reliable cam management.}\end{cvitems} }
\end{cventries}